Papers

### 2023-09-22 quarto/index.qmd
update

* Area Chair
	* *Annual Meeting of the Association for Computational Linguistics* (**ACL**)
	* *Conference on Empirical Methods in Natural Language Processing* (**EMNLP**)

>>>>

* Area Chair
	* *Annual Meeting of the Association for Computational Linguistics* (**ACL**)
	* *Conference on Empirical Methods in Natural Language Processing* (**EMNLP**)
	* *International Conference on Computational Linguistics* (**COLING**)
